Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-17 extended_catalog/paper/extended_catalog.tex
improvements

@@

We found very good agreement between the two methods. For the new
extended source candidates, table~\ref{alt_diff_model_results} shows
a comparison of \ts and \tsext computed using \pointlike and \gtlike.
Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
were calculated using \gtlike using \pointlike's positions and extensions.

@@

The spatial shape of extended sources can e modeled
as a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF for typical sizes look very similar.  Even
though these shapes are significantly different, we demonstrate in
figure~\ref{compare_disk_gauss} that the convolution of shows the
PSF that would be observed for a power-law source of spectral index
2, the probability density function (PDF) for a Gaussian and uniform
disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
The figure shows the convolution for the PSF in the energy range between
1 \gev and 100 \gev and also in the energy range between 10 \gev and
100 \gev.  The convolved shapes do separate better at higher energy, but
nevertheless this plot shows that we are not very sensitive to probing
the exact structure of an extended source.  In this paper we always
assume a uniform disk spatial model.

@@

This is important when comparing morphologies to other wavelengths
because the quoted size can vary significantly depending on which quanity
is reported.  This effect can be best seen in figure~\ref{compare_r68}
which a counts map of an extended source simulated in the energy
range from 1 \gev to 100 \gev with a uniform disk spatial model and
$\sigma=05$. Overlaid on the plot is the fit extension assuming the
source has a uniform disk and a Gaussian spatial model. The plot overlays
both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
the disk spatial hypothesis compared to the Gaussian spatial model. On
the other hand, the disk and Gaussian's 68\% containment radius are
very similar.

@@

As was shown, we gain very little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and susceptible to incorrect modeling of the
galactic diffuse emission.  For that reason, we performed our search
using photons only between 1 \gev and 100 \gev.

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and is
likely not perfectly modeled. On the other hand, at the highest energies
accessible by the LAT, the galactic diffuse emission will be smaller and
we might expect to detect significantly harder sources. This approach is
also beneficial because harder sources with nearby neighbors that are
softer may end up being incorrectly fit at lower energies but correctly
found looking only at the high energy.  This is also beneficial in the
galactic plane looking for possible extended sources near pulsars which
are very bright at lower energy but cutoff before 10 \gev.  This approach
of using only photons with energy above 10 \gev was successfully used
to detecting HESS J1825-137 with the LAT (\cite{fermi_hess_j1825}).

@@

We expect most extended sources to be inside the galactic plane
since extragalactic sources are typically too far away to be
resolvable. Unfortunately, the \gev emission in the galactic plane
is dominated by anisotropic galactic diffuse emission.  Modeling the
galactic diffuse emission and finding sources on top of this emission is
difficult~\ref{first_diffuse_paper}. This issue has been discussed in the
Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
very crowded and so it is often difficult to get a good model for the
region around a catalog source.  Because of this, finding a source with
$\tsext>16$ is not a sufficient test and we perform several crosschecks
to ensure our overall region is well modeled.

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this issue, we describe our test of 
2FGL J1856.2+0450c for
extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
emission subtracted.  A two year catalog source 
2FGL J1856.2+0450c was found at the
position $(l,b)=(37.79\deg,1.14\deg)$.  
We find that there appears to be overall some large scale residual in the
diffuse emission along the galactic plane. Furthermore, it appears that
we don't have a great model of the nearby catalog sources. As a result,
2FGL J1856.2+0450c fits to a very large extension of 1.37\deg and the result is
statistically significant with \tsext=51.6.  By looking at the residuals,
it is clear that this complicated region is not well fit even though
the source's extension is statistically significant. For this reason,
we have to perform a series of followup analysis for all of the sources
that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Using photons with energies greater than 1 \gev, our analysis succesfully
fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
Using photons with energy above 10 \gev, we were able to succesffuly
fit the extesion of HESS J1825-137.
Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the publisehed result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all evnets above 6\gev. Looking at all photons with
energy above 1\gev 
is problematic because of background source confusion whereas using photons
with energy above 10\gev does not have the statistics for a significant dection.

@@

To validate our method and assess systematic issues with our analysis,
we used \pointlike to test known active galaxies (AGN) for extension.
\gev emission from AGN is believed to comes from the core of supermassive
blackholes in small regions in the core of distant galaxies.  AGN are
not expected to be spatially resolvable and therefore provide a good
calibration source to demonstrate the efficacy of our tool. Nevertheless,
it would be very interesting if AGN could be spatially resolved and
there are theories that predict this (\cite{pair_halo_paper}).

@@

The final effect that could cause this discrepancy is an imperfect
modeling of the PSF.  Before launch, the PSF
was determined by a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using very bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization was used in our instrument
response function.
%\footnote{
%LAT Collaboraiton publication pending.
%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
%}. 
But our current parameterization is not perfect. There are lingering
issues due to a lack of statistics at high energy which makes it hard to
validate the PSF as a function of the incident angle of the photon. Since
the distribution of incident angles varies from source to source, an
average PSF may make some of the sources look more and less extended
than the PSF.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

Eight new extended sources not included in the two year catalog were
found using this search. Three were found in our search using events
above 1 \gev and five were found in the search using events
above 10 \gev.
For all the extended sources, the results of our fit are summarized in
table~\ref{new_ext_srcs_table}. The table includes the best fit position and
extension of the source. It also includes the source's significance and
significance of extension.

\subsection{2FGL J1627.0-2425c}
\label{section_ophiuchus}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons between 1 \gev and 100 \gev.
The best fit extension was $0.53\deg\pm0.06\deg$ and the best fit position
is $(l,b)=(352.87\deg, 16.79\deg)$ The source also appeared in the first
fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
was $\tsext=21.1$.  A counts map showing this source is seen in
figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion, we also
fit this region as two point sources. Since $\tsinc=16.6$ is smaller
than \tsext, the emission is more likeliy to come from an extended source.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane, the source is on top
of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are very bright in the infrared.  We have
overlaid on the plot of figure~\ref{1FGL_J1628.6-2419c} a 100 micrometer
infared image of this region as seen by IRAS and there is good spatial
overlap between with the \gev observed emission
(\cite{iras_rho_ophiuci}).

The region has abundant molecular and atomic gas traced by CO and HI but
also plenty of dark gas, the kind that we find only by its association
with dust emission. Embedded star-forming regions make it even more
challenging to measure the column density of dust.
Although this region is significantly extended, we conclude that what
we are seeing is most likely an inadequacy in the diffuse $\gamma$-ray
emission model.

\todo[inline]{Can we get another citation about dark gas
and stuff?
Better note about spectral index being typical of difuse emission.
Also does this description make sense? Also, is 
citation about IRAS good?}

\subsection{2FGL J1554.4-5317c}

@@

The two year catalog source 2FGL J1554.4-5317c was found to be extended
using photons with energy between 1 \gev and 100 \gev.  We found an
extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
$\tsext=39.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
source 2FGL J1551.3-5333c which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. 
These soruce modifications are further described
in the caption to figure~\ref{1FGL_J1554.0-5345c}.

We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source to the increase in log likelihood fitting the region
as two point sources. Since $\tsinc=10.2$ is smaller than \tsext, we
conclude that the source is spatially extended and not multiple point
sources. More information about the dual localization results for this
source are shown in table \ref{dual_localization_results}.

There are no obvious counterparts to this source. Furthermore, this
source is relativly soft with a spectral index 2.31 and very close to
the galacitc plane in a region of large diffuse emission.  We conclude
that although this region is significantly extended, it most likely
represents unmodeled diffuse emission.
\todo[inline]{this needs more quantification/description.
Improve the point about how since the source is soft, it
is more consistent with diffuse emission.
}

\subsection{2FGL J0823.0-4246}
\label{section_puppis_a}

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg\pm0.03\deg$ and an extension
significance of $\tsext=49.2$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source.

This source is coincident with the one year catalog source named 1FGL
J0823.3-4248.  To get a good fit of the source, we had to remove the
nearby catalog sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which
are part of the extended emission.  We tested the source for spatial
confusion by fitting it as two point sources. Because $\tsinc=22.3$ is
smaller then \tsext, we believe that this source is spatially extended.
These removed catalog soruces are shown in figure~\ref{1FGL_J0823.3-4248}.

This extended source is spatially coincident with the SNR Puppis A.
Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of
Puppis A (\cite{rosat_puppis_a}). There is good agreement
between the measured radius of $\sigma=0.37$ degrees in \gev and 
the X-ray contours of the source.

\subsection{2FGL J1615.2-5138}

% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% Deleted
%  *P72Y2490 - 2FGL J1620.6-5111c
%  *P72Y2487 - 2FGL J1619.7-5040c
%  *P72Y2496 - 2FGL J1622.8-5006
% Modify 
%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.365,0.005,SkyDir.GALACTIC)
% New source
%  * SkyDir(332.426,-0.331,SkyDir.GALACTIC

The two year catalog source 2FGL J1615.2-5138 was found to be extended
using photons with energies between 10 \gev and 100 \gev.  This source
is coincident with the one year catalog source 1FGL J1613.6-5100c.
We found an extension of $0.43\deg\pm0.04\deg$ with an extension
significance of \tsext=45.3.  The source was fit to a position of
$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
a counts map of this source.

To get a good fit for the region, we had to remove from our model
the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
position and extension of 2FGL J1615.2-5138.  We ended up with a best
fit position of the nearby source 2FGL J1615.0-5051 having moved from
$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
had to add a new source not in the catalog at the position of
$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
fitting the position of these sources as well as the extension of 2FGL
J1615.2-5138 until a stable fit was found.  It is unclear of this new seed
is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
2FGL J1615.0-5051 was not found to be significantly extended using two
years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
large to obsorb residual in the direction of J1615.2-5138 until we added
the additional point source.
These modifications are further described in the caption to 
figure~\ref{1FGL_J1613.6-5100c}.

To address the possibility of source confusion, we compared the likelihood
fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
that \tsinc=30.1 which is smaller then \tsext so we believe that this
is extended emission.

@@

\subsection{2FGL J1632.4-4753c}

@@

To get a good fit of the region, we had to remove from our model
the four catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
extended source but there is no indication that the emission of these
sources separates.  Finally, we relocalized the
source 2FGL J1635.4-4717c to a better fit position $(l,b)=(337.230\deg,0.346\deg)$
and the position of 2FGL J1636.3-4740c to the better fit position
$(l,b)=(336.968\deg,-0.066\deg)$ to get a good overall fit of our source.
These modifications are further described in the caption to 
figure~\ref{1FGL_J1632.9-4802c}.

In addition we removed from our region four farther away two year
catalog sources J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
2FGL J1639.8-4921c because they were not significant above 10 \gev.

@@

\todo[inline]{Describe What this source is/What HESS Source it is near}
\todo[inline]{Describe contours overlaid on source}

\subsection{2FGL J2021.5+4026}

>>>>

\todo[inline]{Add note about how difficult lat analysis in
the galactic plane is because of large PSF, low statistics,
and high source density. Describe how it requires a certain amount
of iterative, by eye modifying of the sky model. Not
adequate to simply use 2FGL}

@@

We found good agreement between the two methods. For the new
extended source candidates, table~\ref{alt_diff_model_results} shows
a comparison of \ts and \tsext computed using \pointlike and \gtlike.
Unless explicitly mentioned, all \ts, \tsext, and spectral parameters
were calculated using \gtlike using \pointlike's positions and extensions.

@@

The spatial shape of extended sources can e modeled
as a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF for typical sizes look similar.  Even
though these shapes are significantly different, we demonstrate in
figure~\ref{compare_disk_gauss} that the convolution of shows the
PSF that would be observed for a power-law source of spectral index
2, the probability density function (PDF) for a Gaussian and uniform
disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
The figure shows the convolution for the PSF in the energy range between
1 \gev and 100 \gev and also in the energy range between 10 \gev and
100 \gev.  The convolved shapes do separate better at higher energy, but
nevertheless this plot shows that we are not very sensitive to probing
the exact structure of an extended source.  In this paper we always
assume a uniform disk spatial model.

@@

This is important when comparing morphologies to other wavelengths
because the quoted size can vary significantly depending on which quanity
is reported.  This effect can be best seen in figure~\ref{compare_r68}
which a counts map of an extended source simulated in the energy
range from 1 \gev to 100 \gev with a uniform disk spatial model and
$\sigma=05$. Overlaid on the plot is the fit extension assuming the
source has a uniform disk and a Gaussian spatial model. The plot overlays
both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
the disk spatial hypothesis compared to the Gaussian spatial model. On
the other hand, the disk and Gaussian's 68\% containment radius are
similar.

@@

As was shown, we gain little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and susceptible to incorrect modeling of the
galactic diffuse emission.  For that reason, we performed our search
using photons only between 1 \gev and 100 \gev.

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and is
likely not perfectly modeled. On the other hand, at the highest energies
accessible by the LAT, the galactic diffuse emission will be smaller and
we might expect to detect significantly harder sources. This approach is
also beneficial because harder sources with nearby neighbors that are
softer may end up being incorrectly fit at lower energies but correctly
found looking only at the high energy.  This is also beneficial in the
galactic plane looking for possible extended sources near pulsars which
are bright at lower energy but cutoff before 10 \gev.  This approach
of using only photons with energy above 10 \gev was successfully used
to detecting HESS J1825-137 with the LAT (\cite{fermi_hess_j1825}).

@@

We expect most extended sources to be inside the galactic plane
since extragalactic sources are typically too far away to be
resolvable. Unfortunately, the \gev emission in the galactic plane
is dominated by anisotropic galactic diffuse emission.  Modeling the
galactic diffuse emission and finding sources on top of this emission is
difficult~\ref{first_diffuse_paper}. This issue has been discussed in the
Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
crowded and so it is often difficult to get a good model for the
region around a catalog source.  Because of this, finding a source with
$\tsext>16$ is not a sufficient test and we perform several crosschecks
to ensure our overall region is well modeled.

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this issue, we describe our test of 
2FGL J1856.2+0450c for
extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
emission subtracted.  A two year catalog source 
2FGL J1856.2+0450c was found at the
position $(l,b)=(37.79\deg,1.14\deg)$.  
We find that there appears to be overall some large scale residual in the
diffuse emission along the galactic plane. Furthermore, it appears that
we don't have a great model of the nearby catalog sources. As a result,
2FGL J1856.2+0450c fits to a large extension of 1.37\deg and the result is
statistically significant with \tsext=51.6.  By looking at the residuals,
it is clear that this complicated region is not well fit even though
the source's extension is statistically significant. For this reason,
we have to perform a series of followup analysis for all of the sources
that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Using photons with energies greater than 1 \gev, our analysis succesfully
fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
Using photons with energy above 10 \gev, we were able to succesffuly
fit the extesion of HESS J1825-137.
Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the publisehed result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all evnets above 6\gev. Looking at all photons with
energy above 1 \gev 
is problematic because of background source confusion whereas using photons
with energy above 10 \gev does not have the statistics for a significant dection.

@@

To validate our method and assess systematic issues with our analysis,
we used \pointlike to test known active galaxies (AGN) for extension.
\gev emission from AGN is believed to comes from the core of supermassive
blackholes in small regions in the core of distant galaxies.  AGN are
not expected to be spatially resolvable and therefore provide a good
calibration source to demonstrate the efficacy of our tool. Nevertheless,
it would be interesting if AGN could be spatially resolved and
there are theories that predict this (\cite{pair_halo_paper}).

@@

The final effect that could cause this discrepancy is an imperfect
modeling of the PSF.  Before launch, the PSF
was determined by a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization was used in our instrument
response function.
%\footnote{
%LAT Collaboraiton publication pending.
%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
%}. 
But our current parameterization is not perfect. There are lingering
issues due to a lack of statistics at high energy which makes it hard to
validate the PSF as a function of the incident angle of the photon. Since
the distribution of incident angles varies from source to source, an
average PSF may make some of the sources look more and less extended
than the PSF.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

Eight new extended sources not included in the two year catalog
were found using this search. Three were found in our search using
events above 1 \gev and five were found in the search using events
above 10 \gev.  For all the extended sources, the results of our
fit are summarized in table~\ref{new_ext_srcs_table}. The table
includes for each source the best fit position, extension, spectrum,
source significance, and significance of extension.

For all the extended sources, table~\ref{dual_localization_results}
presents information about the of source confusion by fitting the same
region as two point sources using the dual localization method described
in section~\ref{dual_localization_method}. The table compares \tsext
to \tsinc and summarized the positions and spectra of the two sources.
Finally, table~\ref{alt_diff_model_results} summarized the results of
a crosscheck of the source fitting the region with an alternate diffuse
model described in section~\ref{alt_diff_model_description}.  These tables
show that our extended sources are not likely the result of source confusion
and that they are robust to changing the diffuse emission model.

\subsection{2FGL J0823.0-4246}
\label{section_2FGL_J0823.0-4246}

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg\pm0.03\deg$ and an extension
significance of $\tsext=46.1$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source.  This source is coincident with the one year
catalog source 1FGL J0823.3-4248.

To get a good fit of the region we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
extended emission.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
we conclude that this is an extended source.  The removed catalog sources
are shown in figure~\ref{1FGL_J0823.3-4248}.

This extended source is spatially coincident with the SNR Puppis A.
Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of Puppis
A (\cite{rosat_puppis_a}). There is good agreement between of the X-ray
shape with the fit size in \gev.

\subsection{2FGL J1627.0-2425c}
\label{section_2FGL_J1627.0-2425c}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons with energies between 1 \gev
and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
best fit position is $(l,b)=(352.87\deg, 16.79\deg)$ The source also
appeared in the first LAT catalog as 1FGL J1628.6-2419c.  The extension
significance was $\tsext=20.3$.  A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=19.3$
is smaller than \tsext, we conclude that this is an extended source.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane, the source is on top
of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in the infrared.  We have overlaid
on figure~\ref{1FGL_J1628.6-2419c} contours of the 100 micrometer infared
image of this region measured by IRAS. There is good spatial overlap
with the \gev emission (\cite{iras_rho_ophiuci}).

The region also has abundant molecular and atomic gas traced by CO
and HI but also plenty of dark gas, the kind that we find only by its
association with dust emission. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Although this
region is significantly extended, we conclude that this source most
likely represents inadequacy in the diffuse $\gamma$-ray emission model.

\todo[inline]{Can we get another citation about dark gas and stuff?
Better note about spectral index being typical of difuse emission.
Also does this description make sense?}

\subsection{2FGL J1554.4-5317c}
\label{section_2FGL_J1554.4-5317c}

@@

The two year catalog source 2FGL J1554.4-5317c was found to be extended
using photons with energies between 1 \gev and 100 \gev.  We found an
extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a counts map of this source.
This source was found in the one year catalog with the name 1FGL J1554.0-5345c.

To get a good fit of the source, we removed the nearby catalog source
2FGL J1551.3-5333c which is contained within the extended source.
We tested this source for source confusion by fitting it instead
as two point sources.  Since $\tsinc=9.2$ is less than \tsext,
we conclude that the source is spatially extended. The region is further described in
the caption to figure~\ref{1FGL_J1554.0-5345c}.

There are no obvious counterparts to this source at other
wavelengths. Furthermore, this source is relativly soft with a spectral
index 2.31 and is close to the galacitc plane in a region of large
diffuse emission.  We conclude that although this region is significantly
extended, it is most likely unmodeled diffuse emission.

\todo[inline]{this needs more quantification/description.  Improve the
point about how since the source is soft, it is more consistent with
diffuse emission.}

\subsection{2FGL J0851.7-4635}
\label{section_2FGL_J0851.7-4635}

The two year catalog source 2FGL J0851.7-4635 was found to be
extended using photons with energies between 10 \gev and 100
\gev. We fit an extension of $1.12\deg\pm0.07\deg$ with an extension
significance of $\tsext=76.7$.  The source was fit to a position of
$(l,b)=(266.29\deg,-1.41\deg)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.  This source has no counterparts in the first year
LAT catalog.

To get a good fit of the region, we had to remove three nearby catalog
sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711
which are part of the extended emission.  In addition, we relocalized
the position of two nearby catalog sources 2FGL J0854.7-4501 and 2FGL
J0901.7-4655 to better fit their position at high energies in the presence
of an extended source.  This localization was done iterativly alterantly
fitting the position of these two point sources and the extension of
2FGL J0851.7-4635 until the fit globally converged.  2FGL J0854.7-4501
moved to $(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 moved to
$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further away
catalog source 2FGL J0858.0-4815 beacuse it was not significant above 10
\gev.  After modifying the region, we found that \tsinc=16.2 which is less
than \tsext so we conclude that the source is extended These modifications
are further described in the caption to figure~\ref{Vela_Jr}.

2FGL J0851.7-4635 is spatially coincident with the SNR Vela Jr.  Overlaid
on figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in \tev by
H.E.S.S (\cite{vela_jr_hess}).  The \gev and \tev morphology match well.

\todo[inline]{
Add a better interpreation.
Explain that Vela Jr will be described better in upcoming publication???
}

\subsection{2FGL J1615.0-5051}
\label{section_2FGL_J1615.0-5051}

% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138 % extended source
% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 % extended source
% Deleted
%  *P72Y2490 - 2FGL J1620.6-5111c
%  *P72Y2487 - 2FGL J1619.7-5040c
%  *P72Y2496 - 2FGL J1622.8-5006

\subsection{2FGL J1615.2-5138}
\label{section_2FGL_J1615.2-5138}

% Same modifications as 2FGL J1615.0-5051.

%The two year catalog source 2FGL J1615.2-5138 was found to be extended
%using photons with energies between 10 \gev and 100 \gev.  This source
%is coincident with the one year catalog source 1FGL J1614.7-5138c.
%We found an extension of $0.43\deg\pm0.04\deg$ with an extension
%significance of \tsext=45.3.  The source was fit to a position of
%$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
%a counts map of this source.

%To get a good fit for the region, we had to remove from our model
%the nearby catalog sources 2FGL J1620.6-5111c, 2FGL J1619.7-5040c,
%and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
%iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
%position and extension of 2FGL J1615.2-5138.  We ended up with a best
%fit position of the nearby source 2FGL J1615.0-5051 having moved from
%$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
%had to add a new source not in the catalog at the position of
%$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
%fitting the position of these sources as well as the extension of 2FGL
%J1615.2-5138 until a stable fit was found.  
%These modifications are further described in the caption to 
%figure~\ref{1FGL_J1613.6-5100c}.

%To address the possibility of source confusion, we compared the likelihood
%fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
%that \tsinc=30.1 which is smaller then \tsext so we believe that this
%is extended emission.

\todo[inline]{This section needs to be rewritten}

%This extended source is spatially coincident with the extended source
%HESS J1614-518 which was reported in the H.E.S.S. survey of the Inner
%Galaxy (\cite{HESS_plane_survey}). Overlaid on figure~\ref{1FGL_J1613.6-5100c} are the H.E.S.S
%contours of this source and it can be seen that there is good spatial
%overlap between the LAT and H.E.S.S. emission.
%
%It is unclear if our model around the nearby souce 2FGL J1615.0-5051
%is good. 2FGL J1615.0-5051 is spatially coincident with the extended H.E.S.S.
%source HESS J1616-508 but was not found to be significantly extended
%with our extended source search.
%
%It is unclear if this new source is physically real.
%2FGL J1615.0-5051 fit $\ts=28$ and the added source had $\ts=12$
%which is not extended.
%2FGL J1615.0-5051 was not found to be significantly extended.
%$\ts=12$ which is not significant. 
%
%It is unclear of this new seed
%is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
%2FGL J1615.0-5051 was not found to be significantly extended using two
%years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
%large to obsorb residual in the direction of J1615.2-5138 until we added
%the additional point source.
%
%
%HESS J1616-508

@@

\subsection{2FGL J1632.4-4753c}
\label{section_2FGL_J1632.4-4753c}

@@

To get a good fit of the region, we had to remove from our model
the three catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
extended source but there is no indication that the emission of these
sources separates.  Finally, we relocalized the
source 2FGL J1635.4-4717c to a better fit position $(l,b)=(337.230\deg,0.346\deg)$
and the position of 2FGL J1636.3-4740c to the better fit position
$(l,b)=(336.968\deg,-0.066\deg)$ to get a good overall fit of our source.
These modifications are further described in the caption to 
figure~\ref{1FGL_J1632.9-4802c}.

In addition we removed from our region four farther away two year
catalog sources 2FGL J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
2FGL J1639.8-4921c because they were not significant above 10 \gev.

@@

This extended source is spatially coincident with
the \tev source HESS J1634-472.  Overlaid on the counts map are the
contours of the region as seen in \tev (\cite{HESS_plane_survey})
and we see that there is good spatial overlap of these sources.

\todo[inline]{Describe the interpretation of this source}

\subsection{2FGL J1837.3-0700c}
\label{section_2FGL_J1837.3-0700c}
